Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-06 paper.tex
aws images side by side
motivacion modificada

\abstract{The use of accelerators in order to reduce the execution time of some 
application has become more popular during last years. These devices increment 
the computational power of a node thanks to its parallel architecture. %The popularity of the GPGPU computation 
This trend has led several cloud vendors such as Amazon Web Services or some 
middlewares such as OpenStack to add to their current facilities, or to allow, 
instances of virtual machines equipped with NVIDIA GPUs. 
Accomplishing this requirements needs that the guest hosts must be equipped with 
GPUs which could be barely utilized if a non GPU-enabled Virtual Machine is running in the host.
The solution presented in this work is based on GPU virtualization and shareability 
in order to reach an equilibrium between supply and demand of accelerators from the users. 
Hence, we propose to decouple from the nodes, real GPUs by using the virtualization technology called rCUDA. 
With this software configuration, these GPUs can be accessed from any VM getting rid 
of the necessity of having physical GPUs in the guest host. 
Moreover, our project studies the viability of these join by using a public cloud 
service configuration and develops a module for OpenStack middleware in order to 
add the needed support for the virtualized devices and the logic to manage them.. 
The results show a feasible configuration which adds flexibility to the current and well-known 
cloud solutions. 
}

@@

\section{Motivation}
\label{sec:motivation}
Nowadays, to provide a virtual machine with GPUs means
that the guest host must be equipped with at least a GPU, and
once it has been assigned to an instance, no other VM can use
it. Depending on the users’ necessities, two approaches to introduce GPGPU computation in the cluster can be determined:
the conservative, to have a lot of hosts with GPUs to be
ensured that you are likely to satisfy all the requests; or a
more daring approach, where you will count with some GPU-
enabled nodes hoping not to arrive a large burst of requests
so the cluster would run out of GPU resources.

>>>>

\abstract{The use of accelerators in order to reduce the execution time of some 
application has become more popular during last years. These devices increment 
the computational power of a node thanks to its parallel architecture. %The popularity of the GPGPU computation 
This trend has led several cloud vendors such as Amazon Web Services or some 
middlewares such as OpenStack to add to their current facilities, or to allow, 
instances of virtual machines equipped with NVIDIA GPUs. 
Accomplishing this requirements needs that the guest hosts must be equipped with 
GPUs which could be barely utilized if a non GPU-enabled Virtual Machine is running in the host.
The solution presented in this work is based on GPU virtualization and shareability 
in order to reach an equilibrium between supply and demand of accelerators from the users. 
Hence, we propose to decouple from the nodes, real GPUs by using the virtualization technology called rCUDA. 
With this software configuration, these GPUs can be accessed from any VM getting rid 
of the necessity of having physical GPUs in the guest host. 
Moreover, our project studies the viability of these join by using a public cloud 
service configuration and develops a module for OpenStack middleware in order to 
add the needed support for the virtualized devices and the logic to manage them. 
The results show a feasible configuration which adds flexibility to the current and well-known 
cloud solutions. 
}

@@

\section{Motivation}
\label{sec:motivation}

Cloud computing, storage and other facilities are becoming 
more popular during the last years thanks to the easy set up 
process and the low required IT invest. The features provided 
by the cloud vendors are useful for companies and individuals 
which have access to the last technology without spending a 
huge amount of money. Moreover, the systems offered by the cloud 
companies matches with the ones required thanks to its flexibility.

The power of current cloud vendors is based on the use 
of Virtual Machines (VM) which resides inside the host machine and 
emulates a physical node with its own 
cpus, storage, network interconnection, OS and GPU. 
However, to provide a VM with GPUs means
that the guest host must be equipped with at least one GPU, and
once it has been assigned to an instance, no other VM can use
it.

Depending on the users’ necessities, two approaches to introduce GPGPU computation in the cluster can be determined:
the conservative, to have a lot of hosts with GPUs to be
ensured that you are likely to satisfy all the requests; or a
more daring approach, where you will count with some GPU-
enabled nodes hoping not to arrive a large burst of requests
so the cluster would run out of GPU resources.
